### 2022-04-22 paper/ase22/experiment.tex
exp

\begin{enumerate}[label=\textbf{RQ\arabic*}]
\item \label{rq:one}: Can \tool generate sentences consistent to their
  sentiment label and their target \lc?
\item \label{rq:two}: Can \tool find different bugs from \Cklst?
\item \label{rq:three}: Can the \tool generated testcases have stronger
  generalization ability to test NLP models?
\item \label{rq:four}: Can \tool be useful to find root of bug in the
  NLP models?
%% \item \label{rq:three}: How effective is our new test case generation
%%   using \cfg expansion? % ablation study
\end{enumerate}

@@

First, \tool generates sentences and its label by empirical reasoning
derived from \lc statements. Therefore, we meaure acceptibility of the
testcases by verifying the relevancy between sentence and label, and
between sentence and its \lc. The RQ~\ref{rq:one} thereby is answered
by verifying the quality of generated testcases. In this work, we
conduct manual study and measure the correlation of human labeled
testcases and \tool labeled testcases.

Second, evaluation on testcases more equivalent to real world
estimates model performance in practical use more accurately. It means
more various bugs from the input distribution are likely to be
captured.  On the other hand, limited distribution only represents
narrow or uncommon portion of real world, and it leads to detect bugs
within the restricted range. As a result, retraining a model on the
testcases within  obtains lower

debugs less various bugs.

To answer the RQ~\ref{rq:two}, we retrain
a NLP model on generated testcases and analyze the retraining performance.

it means that retraining model on more
generalized testcases can debug more various bugs found in the
original model.

To answer the RQ~\ref{rq:two}, we retrain a NLP model on generated testcases.

Third, the amount of NLP
model component executed during testing is also critical measurement
for assessing quality of software testing. A high software coverage
results in lower chances of unidentified bugs in the NLP
model. Accordingly, the ability of testcases to produce high portion
of model coverage needs to be measured and answer the
RQ~\ref{rq:three}.

In addition to the detection of bugs in the model,
explaination of the bugs is also important stage of debugging and
repairing the model. Therefore, we anwer RQ~\ref{rq:four} by showing
usefulness of \tool by analyzing the NLP model based on \tool and
finding root of the bug.

\subsection{Experiment Setup}

To resolve these, we conduct practical experiments and show the
effectiveness of \tool. We conduct a maual studyRQ~\ref{rq:one}

we generate test cases and use
them for evaluating model on linguistic capabilities. In this
experiment, We assess the ability to find failures by anlyzing model's
performance on the generated test cases. We also measure the diversity
among the generated test cases using similarites among them. Next, we
answer \ref{rq:three} by retraining \sa model with generated test
cases and measuring performances. The idea behind this is that more
comprehensive inputs becomes closer to real-world distribution and
addresses more type of errors.  Therefore, it leads to improve the
model performance. In this experiment, We retrain the model and
compare performances of the retrained model. Not only that, we conduct
ablation study of \cfg expansion to understand the its impact in our
approach.

>>>>

\begin{enumerate}[label=\textbf{RQ\arabic*}]
\item \label{rq:one}: Can \tool generate sentences consistent to their
  sentiment label and their target \lc?
\item \label{rq:two}: Can the \tool generated testcases have stronger
  generalization ability to test NLP models?
\item \label{rq:three}: Can \tool be useful to find root of bug in the
  NLP models?
%% \item \label{rq:three}: How effective is our new test case generation
%%   using \cfg expansion? % ablation study
\end{enumerate}

@@

First, \tool generates sentences and its label by empirical reasoning
derived from \lc statements. Therefore, we meaure acceptibility of the
testcases by verifying the relevancy between sentence and label, and
between sentence and its \lc. The RQ~\ref{rq:one} thereby is answered
by verifying the quality of generated testcases. In this work, we
conduct manual study and measure the correlation of human labeled
testcases and \tool labeled testcases. Second, the amount of NLP model
component executed during testing is a critical measurement for
assessing quality of software testing. A high software coverage
results in higher chances of unidentified bugs in the NLP model. On
the other hand, limited distribution only represents narrow portion of
real world covering limited execution paths in a NLP model. It leads
to detect bugs within the restricted execution paths.  Therefore,
testcases more equivalent to real world represents more generalized
distribution, and it results in high coverage of the NLP model.
Accordingly, the ability of testcases to produce high portion of model
coverage needs to be measured. We answer the RQ~\ref{rq:three}
measuring neural coverage of the neural NLP model according to the
measurements. In addition to the detection of bugs in the model,
explaination of the bugs is also important stage of debugging and
repairing the model. Therefore, we anwer RQ~\ref{rq:four} by showing
usefulness of \tool by analyzing the NLP model based on \tool and
finding root of the bug.

\subsection{Experiment Setup}
We conduct practical experiments and show the effectiveness of
\tool.

\subsubsection{Manual study}
We sample set of test cases and corresponding \lc randomly sampled
from seed sentences and expanded sentences from \tool.  Subjects are
also provided with the sampled testcases. Each subject is asked for
scoring relevancy between the linguistic capability of the
sentences. The scores range from 1 to 5 representing strongly not
relevant to strongly relevant respectively. Additionally, the subject
scores the relevancy between sentences and their sentiment labels. The
scores also range from 1 to 5, and they represent strongly negative to
strongly positive respectively. In this work, we collect manual study
scores from {} subjects attended. From the collected scores, we
measure the following metrics:

\begin{enumerate}[label=\textbf{Metrics}]
\item \label{mm:one} Reported bugs
\item \label{mm:two} Incorrect inputs
\item \label{mm:three} Label Inconsistency
%% \item \label{rq:three}: How effective is our new test case generation
%%   using \cfg expansion? % ablation study
\end{enumerate}

The metrics used for this study
